---
title: "UK Energy Consumption Forecast with ETS Methods"
author: "Teik Keat Tee"
date: "2023-12-12"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***

## 1. Introduction and Data Description
The time series data of interest for this assignment is UK's Historical Electricity Demand from 2013 to 2022, which is a published data source obtained from [**UK National Grid ESO**](https://www.nationalgrideso.com/data-portal/historic-demand-data?page=0).

The original data contains a bi-hourly recorded series of energy demand, wind, solar data etc., where we are only interested in the columns 'settlement_date' and 'nd'.

The bi-hourly recorded series will be first aggregated into **daily** frequency based on 'settlement_date'. Then, the **monthly** series will be obtained through averaging the daily series, as this eliminates the effect of different calendar days in each month.

The reason for our selection of monthly forecasting in our exercise is mainly due to the restriction from the complexity of daily series forecasting, which is unable to be handled by the models under the scope of this assignment. These difficulties arise from multi-seasonality effects and noises in daily series (see appendix 9.1). Therefore, aggregating the data to monthly level makes it more manageable.

The column 'nd' contains sum of metered power generation, excluding generation required to meet station load, pump storage pumping and interconnector exports. This complies with National Grid ESO operational generation metering and the Great Britain generation reporting requirement. The electricity demand is measured in MW (megawatts).

The 10 years time-frame has been selected due to its perseverance of any cyclical dynamics, although we do not observed it in the analysis.

*\* Note that to achieve brevity and ensure originality, the raw csv files were pre-processed by simply combining the yearly publication into one csv file manually. However, further data processing will be done in Section 2.*

***

## 2. Preliminaries
Prior to the analyses, some preliminary steps should be taken care of. These include data extraction and processing, as well as importing dependencies.

## 2.1 Import Dependencies
```{r import_dependencies, message=FALSE}
library(fpp3) # [v0.5] For analysing, plotting, forecasting, data wrangling etc.
```

## 2.2 Data Extraction and Processing
```{r data_extract, message=FALSE}
# Extracting the raw data from github to a data frame
# Truncating the file path to ensure visibility
elec_raw_df <- data.frame(
  read.csv(paste0("https://raw.githubusercontent.com/teikkeat80/", 
  "UK_Energy_Consumption_Forecast_ETS/main/energy_data/uk_elec_2012_2022.csv")))

# Extracting the subset of data of interest mentioned in Section 1.
elec_df <- elec_raw_df %>% 
  select(settlement_date, nd) %>% 
  # Aggregation of demand into gigawatt (GW) since here we are looking 
  # at a national daily level
  mutate(nd = nd * 10^-3) %>% 
  group_by(settlement_date) %>% 
  summarise(nd = sum(nd))
  
# Rename columns for better coding practice
colnames(elec_df) <- c("date", "demand")

# Convert dataset to suitable time series
elec_ts_daily <- elec_df %>% 
  mutate(
    # Convert date column with different date format to date type variables
    # The change of date format was due to change of reporting format since 2022
    date = ifelse(grepl(".*-[A-Z]*-.*", date), 
                  as.Date(date, format = "%d-%h-%Y"), 
                  as.Date(date, format = "%Y-%m-%d")),
    date = as.Date(date, origin = "1970-01-01")) %>% 
  arrange(date) %>% 
  as_tsibble(index = date)
  
# Aggregating data series into monthly series
elec_ts_monthly <- elec_ts_daily %>% 
  mutate(month = yearmonth(date), 
         demand = round(demand, 2)) %>% 
  as_tibble() %>% 
  select(-date) %>% 
  group_by(month) %>% 
  summarise(demand = mean(demand)) %>% 
  as_tsibble(index = month)
```

The dependencies and processed time series data are now ready for the analysis. Our prepared data set here contains 120 observations.

***

## 3. Visualisations and Exploratory Data Analysis

The following plots were produced to illustrate the dynamics of our data concerning UK's electricity consumption.

- Monthly time plot
- Yearly seasonal plot

As the monthly data series is of main interest, the monthly plot is simply the time plot.

*\* Note that we have also provided the daily time plot and weekly seasonal plot in appendix 9.1 to explain the reasoning behind carrying out monthly forecasting as the focus of our exercise.*

```{r time_plot, fig.width=5, fig.height=4}
# Generating monthly plot using autoplot()
elec_ts_monthly %>% 
  autoplot(demand) + 
  labs(title = "UK Electricity Demand Monthly Plot", 
       subtitle = "From Jan 2013 to Dec 2022", 
       y = "Averaged Electricity Demand (GW)", 
       x = "Month")
```

From the monthly time plot itself, we can clearly observe a yearly seasonal pattern in the UK National Electricity Demand series. The seasonal pattern can be mainly attributed to the varying electricity consumption in different weathers, which will be explained further in the seasonal plot analysis. Furthermore, the seasonal pattern observed here seems to be in similar magnitude for each season; such additive behaviour will be modeled into our forecasting methods later.

Besides, the series exhibits a downwards trend over the decade, where it begins to become flattened from 2017 onwards (if we ignore 2020 and 2022). The main reason behind this was the introduction of a series of energy efficient policies by the UK government throughout these years, which managed to control national-level electricity consumption while promoting sustainability. Examples of these policies in place include the introduction of effective efficiency improvement schemes (such as ECO, MEES, etc.), and implementation of advanced technologies such as smart electrical appliances. Despite the success of these policies, there remained an upside drive by digitalisation and increasing population especially in later years, which explains the flattened trend.

We also observe a significant drop in the magnitude of electricity demand during year 2020. This is attributed to the initial lockdown which UK government enforced in response to the COVID-19 outbreak. Many businesses including services, commercials and industrial sectors were forced to shut down, and subsequently reduced the national electricity consumption. A bounce back occurred later in the year when these restrictions were removed. Apart from this, another significant drop in electricity demand had occurred during the first half of the year of 2022. This was in light of the geopolitical-driven energy crisis, where the electricity prices had been surging due to supply-side factors (e.g. Russian-Ukraine Conflict). We keep this in mind during our analysis.

The monthly time plot summarises the overall pattern of UK's electricity demand from year 2013 to 2022. Next, we will be looking at the yearly seasonal plot.

```{r seasonal_plot_yearly, fig.width=5, fig.height=4}
# Generating yearly seasonal plot using gg_season
elec_ts_monthly %>% 
  gg_season(demand, period = "year") + 
  labs(title = "UK Electricity Demand Yearly Seasonal Plot", 
       subtitle = "From Jan 2013 to Dec 2022", 
       y = "Averaged Electricity Demand (GW)", 
       x = "Month")
```

As suggested from the monthly time plot, the UK Electricity Consumption series demonstrates a yearly seasonality. The seasonal plot shows that there is a decreasing trend from the beginning of each year until July, while it increases again towards the end of the year. This is mainly due to the additional electricity consumption during winter days. 

Winter begins around November, where temperature can potentially drop to around -3 to 7 Degree Celsius. The high electricity consumption is mainly attributed to the widespread usage of electrical heating devices and increasing lighting usage (as daylight time is shorter). Peak electricity consumption is usually observed in January.

The electricity consumption gradually decreases as temperature increases and daylight time becomes longer, where the demand hits lowest during summer (July). Interestingly, this contrasts with the phenomenon seen in other locations with seasonal weather (e.g. Australia). This is because most UK buildings generally does not have built-in cooling systems due to a much milder summer.

Apart from that, we can also observe that there is a slight drop in electricity consumption in the month of December for some years, which reflects the effect of holiday seasons (Christmas and New Year), where companies and offices are closed for celebrations.

***

## 4. Forecast with Holt-Winters' Method

From this section onwards, we model the data series in an experimental manner by employing several appropriate models. Then, we evaluate the forecasting performance of our models. To do this, we first split our data into training and testing samples using the common 70:30 ratio, where we leave the last 3 years of our data for testing purpose. This ensures a reliable indication of the accuracy of the fitted model.

```{r tts}
# Split into train and test set
elec_train <- elec_ts_monthly %>% 
  filter_index(. ~ "2019-12-31")

elec_test <- elec_ts_monthly %>% 
  filter_index("2020-01-01" ~ .)
```

Given the exploratory data analysis in Section 3, we have observed an **additive** seasonal behaviour from our data series. Apart from that, we have also observed a diminishing trend behaviour towards recent years. As such, we first consider the **Holt-Winters' Additive with Damped Trend method**.

```{r hwad_fit_fc, fig.width=5, fig.height=4}
# Fitting the model
elec_fit_hwad <- elec_train %>% 
  model(hwad = ETS(demand ~ error("A") + trend("Ad") + season("A")))

# Generate model fit report
elec_fit_hwad %>% 
  report()

# Generate forecast
elec_fc_hwad <- elec_fit_hwad %>% 
  forecast(elec_test)

# Plot forecasted series alongside the last few years in the training data
elec_fc_hwad %>% 
  autoplot(filter(elec_train, year(month) > 2017), colour = "red") + 
  autolayer(elec_test, demand, colour = "navy") + 
  labs(y = "Averaged Electricity Demand (GW)", 
       title = "UK's Electricity Demand Forecast",
       subtitle = "with ETS(A,Ad,A)", 
       x = "Month"
       ) + 
  theme_minimal()
```

From the graph above we observe that the forecast with Holt-Winters' Additive and Damped Trend method seems to be rather accurate for the year of 2021, where the bounce back from COVID period tends to be addressed by the damping parameters. However, there seems to be some deviations between the forecasted series and the actual series for the years of 2020 and 2022. This result is consistent with what we have suggested earlier about the crisis periods. Nevertheless, we consider this as one of our tentative models, and evaluate it with other models. Note that we cannot reach any conclusions from this forecast as there remains further work to be done (residual diagnostics and comparative analysis with other models, will address later).

***

## 5. Holt-Winters' Additive/Multiplicative Seasonality

In this section we attempt to describe the additive seasonality that we have employed in more detail.

Including the model in Section 4, most models in this assignment are mostly based on the Holt-Winters' method - which was an extended model from Holt's Linear method (1957) by Holt and Winters (1960). Holt-Winters introduces a seasonal component to capture seasonality. Note that the presence of seasonality is apparent even from visual check, so this rules out models that do not incorporate any form of seasonality (e.g. simple exponential smoothing, whose forecast is flat equal to the last level)

The seasonal component here can be described by two kinds of behaviour, whether it is additive or multiplicative. Additive seasonality is appropriate when the seasonal fluctuations are relatively constant across all levels of the series, while multiplicative seasonality tends to be employed when the magnitude of seasonal variations is proportional to the level of the series. Since the seasonal variation throughout each years in our data series seems to be in a similar magnitude, we are motivated to employ additive instead of multiplicative seasonality for our models. (However, it might also be true that whether additive or multiplicative behaviour could not be easily differentiated by looking at the plots - we will address this later.)

This additive behaviour indicates that the difference between summer and winter electricity usages remains constant. In fact, the differences between the months with highest and lowest electricity consumption throughout the years stay in the range around 32 ~ 43% (with the exception year 2020, see appendix 9.2). Given the time frame (10 years) we consider for our data series, this phenomenon is sensible, as we should assume that a change of climate-driven seasonal pattern such as increasing/decreasing seasonal temperature differences and daylight time could only be detected in time series with longer horizon (e.g. decades).

***

## 6. Additional ETS/Other Models

In this section, we continue to consider several other models and methods.

Apart from the trend and seasonal component, ETS models can be adjusted in a statistical sense by considering the behaviour of errors. The error component can be additive or multiplicative, where the prediction intervals behave differently depending on the type. The identification of the correct kind of errors' behaviour can be done via comparing selection criteria values such as AICc, AIC and BIC. Therefore, we simply employ the automated ETS function in R to determine whether our model fit contains additive or multiplicative errors, where the automated ETS function simply selects the model with lowest AICc values.

```{r auto_fit}
# Fitting the model
elec_fit_auto <- elec_train %>% 
  model(ets_auto = ETS(demand))

# Generate report
elec_fit_auto %>% 
  report()
```

The automated ETS function tends to suggest a similar trend and seasonal component. However, it seems that the multiplicative error tends to provide a better fit. We have observed lower AIC, AICc and BIC values from the multiplicative error model in comparison to additive error model. This can have resulted from the heteroscedasticity in our data series' variances. The effect can be captured by multiplicative error models, and they are also physically appropriate to our use case as electricity demand should not be negative after all. As such, we proceed with multiplicative error models going forward.

Apart from the adjustment in errors, we also employ the Guerrero's method to determine whether there is an optimal lambda that can minimise the variations in our data.

```{r bc_transformation}
# Obtain the Guerrero's lambda
lambda <- elec_train %>% 
  features(demand, features = guerrero) %>% 
  pull(lambda_guerrero)

# Print out result
print(paste0("Guerrero's Lambda: ", round(lambda, 6)))
```

The lambda value of 1.125 (close to 1) suggests that transformation might not be as useful. As a result, we simply do not consider any transformation. We suppose that any kind of variation in our data (e.g. trend/seasonal) should be able to modelled into the ETS models with the correct specifications.

Combining the model and information we have at this point, we employ the following models in our forecasting process:

- ETS (Additive Seasonality and Damped Trend) [ETS(A,Ad,A)]
- ETS (Additive Seasonality and Damped Trend with Multiplicative Errors) [ETS(M,Ad,A)]
- Seasonal Naive [SNAIVE]
- ETS (Additive Seasonality and Damped Trend with Multiplicative Errors) on STL Seasonally Adjusted series [STL+ETS(M,Ad,N)]

```{r all_fit_fc}
# Fit the models
elec_fit_all <- elec_train %>% 
  model(ets_aada = ETS(demand ~ error("A") + trend("Ad") + season("A")), 
        ets_mada = ETS(demand ~ error("M") + trend("Ad") + season("A")), 
        snaive = SNAIVE(demand), 
        ets_madn_stl = decomposition_model(
          STL(demand, robust = TRUE), 
          ETS(season_adjust ~ error("M") + trend("Ad") + season("N"))))

# Generate forecast
elec_fc_all <- elec_fit_all %>% 
  forecast(elec_test)
```

```{r fc_plot_point1, fig.width=5, fig.height=4}
# Generate point forecast plots with more recent years
elec_fc_all %>% 
  autoplot(filter(elec_train, year(month) > 2017), level = NULL) + 
  autolayer(elec_test, demand, colour = "navy") + 
  labs(y = "Averaged Electricity Demand (GW)", 
       title = "Electricity Demand Point Forecasts",
       subtitle = "with Multiple Models", 
       x = "Month") + 
  theme_minimal()
```

From above point forecasts graph, it seems difficult to tell which model has a better forecasting performance, apart from the observation that the seasonal naive model tends to be diverging the most from the actual values. Therefore, we explore these models with a more thorough manner in Section 7.

***

## 7. Forecast and Residual Analysis 

In this section we present a detail in-sample exploration for the all models we have. Then, we evaluate the selected models' (from in-sample analysis) out-of-the-sample forecast accuracy through comparing different forecasting performance metrics.

## 7.1 In-Sample Residual Analysis
In order to determine which model tends to have the best in-sample fit, we evaluate both the residuals' behaviour and the model's information criteria values (AIC, AICc, BIC).

```{r residual_plot1, fig.width=5, fig.height=4, warning=FALSE}
# Generate residuals plots
elec_fit_all %>% 
  select(ets_aada) %>% 
  gg_tsresiduals() + 
  labs(title = "ETS(A,Ad,A) residual plots")
```

```{r residual_plot2, fig.width=5, fig.height=4, warning=FALSE}
# Generate residuals plots
elec_fit_all %>% 
  select(ets_mada) %>% 
  gg_tsresiduals() + 
  labs(title = "ETS(M,Ad,A) residual plots")
```

```{r residual_plot3, fig.width=5, fig.height=4, warning=FALSE}
# Generate residuals plots
elec_fit_all %>% 
  select(snaive) %>% 
  gg_tsresiduals() + 
  labs(title = "SNAIVE residual plots")
```

```{r residual_plot4, fig.width=5, fig.height=4, warning=FALSE}
# Generate residuals plots
elec_fit_all %>% 
  select(ets_madn_stl) %>% 
  gg_tsresiduals() + 
  labs(title = "STL+ETS(M,Ad,N) residual plots")
```

From the residual plots, we observe that apart from SNAIVE, all models seem to have residuals varying around 0 with small variance. Apart from this behaviour, the ACF plots and histograms show that our models' residuals do not conform to a "desirable fitted models' residuals". There seem to be 1st-, 11th-, and 12th-order autocorrelated residuals for all models. Moreover, the histograms do not convince us that the residuals follow the normality assumption. Nevertheless, we employ statistical tests to assess the residual behaviours formally.

```{r residual_diag, message=FALSE, warning=FALSE}
# Mean evaluation
mean_eval_fn <- function (mable) {
  result <- mable %>% 
    augment() %>% 
    as_tibble() %>% 
    group_by(.model) %>% 
    summarise(mean = round(mean(.innov, na.rm = TRUE), 6))
  return(result)
}

elec_fit_mean <- mean_eval_fn(elec_fit_all)

# Autocorrelation evaluation (Ljung-Box Test)
lb_eval_fn <- function (mable) {
  result <- mable %>% 
    augment() %>%  
    # Setting the lag as min{T/5,2m}, where T is the number of observations 
    # and m is the seasonal period 
    features(.innov, ljung_box, lag = min(nrow(elec_train) / 5, 2 * 12)) %>% 
    mutate(lb_stat = round(lb_stat, 6), lb_pvalue = round(lb_pvalue, 6))
  return(result)
}

elec_fit_acf <- lb_eval_fn(elec_fit_all)

# Normality evaluation (Shapiro-Wilk Test)
sw_eval_fn <- function (mable) {
  result <- mable %>% 
    augment() %>% 
    as_tibble() %>% 
    group_by(.model) %>% 
    summarise(sw_stat = round(shapiro.test(.innov)$statistic, 6), 
              sw_pvalue = round(shapiro.test(.innov)$p.value, 6))
  return(result)
}

elec_fit_norm <- sw_eval_fn(elec_fit_all)

# Show residuals diagnostics result
inner_join(elec_fit_mean, 
           inner_join(elec_fit_acf, elec_fit_norm, by = '.model'))
```

From above table, we observe that the mean of residuals tends to be close to zero (apart from the SNAIVE model, which reported a downward bias), thus confirming what we observe from the plots. This result indicates our point forecasts generated by the ETS models is unbiased.

Apart from this, the Portmanteau test result (low p-values/high Ljung-Box statistic) shows that all of the models do not satisfy the white noise assumption. The result is similar to what we observe from the ACF plots. This indicates that there is some information left over in the residuals where our models might not be complete.

Suprisingly, the large p-values from the Shapiro-Wilk normality test shows that our models are somehow satisfying the normal residuals assumptions, where we do not have enough evidence to reject the null hypothesis of normal residuals. The result suggests that the histogram plots might be misleading, and this situation might arise from the lack of data points.

In order to address the bias from the SNAIVE model and autocorrelated residuals from all the models, we employ a trial-and-error approach and consider various transformations and parameter adjustments (for brevity we do not show it here). We find that adding a drift component tends to eliminate the bias from SNAIVE and make it comparable to the rest of the models. 

Besides, we also find that considering a multiplicative seasonality and setting a higher alpha parameter (only for multiplicative error models) tend to increase the chances for the white noise assumption to be true. We select alpha = 0.4 for the best trade-off between residuals' behaviour and AICc results. Note that the multiplicative seasonality corresponds to our earlier discussion on possibly not being able to identify the actual effect through visualisations (or it could also be that we are lacking exogeneous regressors to accompany the additive behaviour, nevertheless, multiplicative seasonality addresses this issue).

```{r, update_model, message=FALSE, warning=FALSE}
# Modification of the model
elec_fit_all_mod <- elec_train %>% 
  model(ets_aadm_mod = ETS(demand + 2 ~ error("A") + trend("Ad") + season("M")), 
        ets_madm_mod = ETS(demand ~ error("M") + trend("Ad", alpha = 0.4) + season("M")), 
        snaive_mod = SNAIVE(demand ~ drift()), 
        ets_madn_stl_mod = decomposition_model(
          STL(demand, robust = TRUE), 
          ETS(season_adjust ~ error("M") + trend("Ad", alpha = 0.4) + season("N"))))

# Statistical Test (Not plotting residuals to save space)
elec_fit_mean_mod <- mean_eval_fn(elec_fit_all_mod)
elec_fit_acf_mod <- lb_eval_fn(elec_fit_all_mod)
elec_fit_norm_mod <- sw_eval_fn(elec_fit_all_mod)

# Show result
inner_join(elec_fit_mean_mod, 
           inner_join(elec_fit_acf_mod, elec_fit_norm_mod, by = '.model'))
```

Through the modifications, we observe that there is a significant reduction in the Ljung-Box statistic for the ETS models, while the mean of SNAIVE with Drift model has reduced to 0. This has been achieved while keeping the unbiased estimator and normality assumption to be true. Note that we have accounted for the small bias for our Additive Error ETS model by adding constant 2 to the demand series. Although the p-values still remain low, this is the best we can achieve under the scope of considering only ETS models. Ultimately, the Ljung-Box test might not provide a desirable outcome after all since we have a long seasonality period (12) and our data points are not as many.

Information Criteria (IC) values such as AIC, AICc, and BIC employ a robust method to minimise the SSE of ETS models, therefore helping us in the model selection process. Next, we examine the AIC, AICc, and BIC of all the ETS models we have until this point.

```{r ic_values_eval}
# Generate table for comparing IC values
elec_fit_all_report <- elec_fit_all %>% 
  # As glance() does not support mix models, we will report it separately
  # SNAIVE won't have IC values
  select(-ets_madn_stl, -snaive) %>% 
  glance() %>% 
  select(.model, AIC, AICc, BIC)

elec_fit_all_mod_report <- elec_fit_all_mod %>% 
  select(-ets_madn_stl_mod, -snaive_mod) %>% 
  glance() %>% 
  select(.model, AIC, AICc, BIC)

# Show result
rbind(elec_fit_all_report, elec_fit_all_mod_report)

# Show mix-models results individually
elec_fit_all %>% 
  select(ets_madn_stl) %>% 
  report()

elec_fit_all_mod %>% 
  select(ets_madn_stl_mod) %>% 
  report()
```

From above information, it seems that the modifications have slightly increased the AIC, AICc, and BIC values of all the non-mixed models. However, we notice that for some models, this trade-off is relatively minimal for getting a better residuals' behaviour. Note that we do not directly compare the IC values of the STL-mixed models with other ETS models, as the IC values from mixed-model were only calculated against the seasonal adjusted series instead of the demand series itself. Given above results, the model selection process is subjective. We therefore select the following models for forecast performance evaluation:

- ETS(A,Ad,M) : The modified version, as it gives a much lower Ljung-Box statistic.
- ETS(M,Ad,A) : Lowest IC values among all non-mixed ETS model, the modified version trade-off does not seems too desirable.
- SNAIVE with Drift : Simply makes sense and it is more comparable.
- STL+ETS(M,Ad,N) : The modified version is better in all terms (IC values and Residual behaviour).

```{r final_fit}
# Fit model for our selected models
elec_fit_all_final <- elec_train %>% 
  model(ets_mada = ETS(demand ~ error("M") + trend("Ad") + season("A")), 
        ets_aadm_mod = ETS(demand + 2 ~ error("A") + trend("Ad") + season("M")), 
        snaive_mod = SNAIVE(demand ~ drift()), 
        ets_madn_stl_mod = decomposition_model(
          STL(demand, robust = TRUE), 
          ETS(season_adjust ~ error("M") + trend("Ad", alpha = 0.4) + season("N"))))
```

## 7.2 Out-of-the-Sample Forecast Performance Analysis
Next, we evaluate the forecast performance of the selected models from Section 7.1 using the test data. As all models here satisfy the normality assumption, we consider their prediction intervals in a simpler manner (i.e. not considering bootstrap etc.).

```{r fc_plot_point2, fig.width=5, fig.height=4}
# Generate forecasts
elec_fc_all_final <- elec_fit_all_final %>% 
  forecast(elec_test)

# Generate point forecast plots with more recent years
elec_fc_all_final %>% 
  autoplot(filter(elec_train, year(month) > 2017), level = NULL) + 
  autolayer(elec_test, demand, colour = "navy") + 
  labs(y = "Averaged Electricity Demand (GW)", 
       title = "Electricity Demand Point Forecasts",
       subtitle = "with Multiple Models (Final)", 
       x = "Month") + 
  theme_minimal()
```

Similarly, the point forecast plot does not convey too much information. However, it shows that there is a better performance for the SNAIVE with drift model comparing to the original SNAIVE model. Besides, in terms of the ETS models, we also observe that the STL+ETS(M,Ad,N) model tends to depart the most from the peaks, whereas ETS(A,Ad,M) model tends to depart the most from the troughs. Nevertheless, to critically assess the performance of the models, we consider the interval forecast plots and the accuracy measures.

```{r fc_int_plot1, fig.width=5, fig.height=4}
# Generate interval forecast plots for ETS(M,Ad,A)
elec_fc_all_final %>% 
  filter(.model == "ets_mada") %>% 
  autoplot(filter(elec_train, year(month) > 2017), colour = "red") + 
  autolayer(elec_test, demand, colour = "navy") + 
  labs(y = "Averaged Electricity Demand (GW)", 
       title = "Electricity Demand Interval Forecasts",
       subtitle = "with ETS(M,Ad,A)", 
       x = "Month") + 
  theme_minimal()
```

```{r fc_int_plot2, fig.width=5, fig.height=4}
# Generate interval forecast plots for ETS(A,Ad,M)
elec_fc_all_final %>% 
  filter(.model == "ets_aadm_mod") %>% 
  autoplot(filter(elec_train, year(month) > 2017), colour = "red") + 
  autolayer(elec_test, demand, colour = "navy") + 
  labs(y = "Averaged Electricity Demand (GW)", 
       title = "Electricity Demand Interval Forecasts",
       subtitle = "with ETS(A,Ad,M)", 
       x = "Month") + 
  theme_minimal()
```

```{r fc_int_plot3, fig.width=5, fig.height=4}
# Generate interval forecast plots for ETS(M,Ad,A)
elec_fc_all_final %>% 
  filter(.model == "ets_madn_stl_mod") %>% 
  autoplot(filter(elec_train, year(month) > 2017), colour = "red") + 
  autolayer(elec_test, demand, colour = "navy") + 
  labs(y = "Averaged Electricity Demand (GW)", 
       title = "Electricity Demand Interval Forecasts",
       subtitle = "with STL+ETS(M,Ad,N)", 
       x = "Month") + 
  theme_minimal()
```

```{r fc_int_plot4, fig.width=5, fig.height=4}
# Generate interval forecast plots for ETS(M,Ad,A)
elec_fc_all_final %>% 
  filter(.model == "snaive_mod") %>% 
  autoplot(filter(elec_train, year(month) > 2017), colour = "red") + 
  autolayer(elec_test, demand, colour = "navy") + 
  labs(y = "Averaged Electricity Demand (GW)", 
       title = "Electricity Demand Interval Forecasts",
       subtitle = "with SNAIVE with Drift", 
       x = "Month") + 
  theme_minimal()
```

```{r fc_analysis, fig.width=5, fig.height=4}
# Generate accuracy table
accuracy(elec_fc_all_final, elec_test)

# Generate accuracy table for non-crisis period
accuracy(filter(elec_fc_all_final, year(month) == 2021), 
         filter(elec_test, year(month) == 2021))
```

According to the plots, it seems that apart from the ETS(M,Ad,A) model and year of 2020, all actual values from the test data seem to lie in the 95% confidence interval. In terms of their relative point forecasts, ETS(M,Ad,A) and SNAIVE with Drift seem to be more accurate than others. However, the increasing width of the prediction intervals for SNAIVE with Drift and ETS(A,Ad,M) implies the large uncertainty for the forecasts when we are looking at further periods.

In terms of the accuracy table, the result is somehow suprising. SNAIVE with Drift Method seems to have the lowest RMSE and MAE, followed by ETS(M,Ad,A) model. Nevertheless, this was due to the crisis period in 2020 and 2022 in our test dataset, where the deviations from the ETS models' forecasts to actual values tend to be large. As it makes no sense to conclude which model is better during crisis periods (anything can happen), therefore, we separate the test data and examine only on the non-crisis period (i.e., year 2021). The result is convincing, as we observe **ETS(M,Ad,A)** tends to provide the best out-of-the-sample forecast in terms of RMSE and MAE, followed by STL+ETS(M,Ad,N), and the basic SNAIVE with Drift model is the worst.

***

## 8. Conclusion and remarks

From the residual analysis above, we have shortlisted 4 candidate models, namely ETS(M,Ad,A), Modified STL+ETS(M,Ad,N), SNAIVE with Drift, and Modified ETS(A,Ad,M). The Modified ETS(A,Ad,M) demonstrates the best residual behaviour, while ETS(M,Ad,A) provides the lowest IC values in terms of all single ETS models. Regarding the mixed-models, the modified STL+ETS(M,Ad,N) model is better than the non-modified STL+ETS(M,Ad,N).

Nevertheless, the whole process and modelling could be improved as we somehow do not manage to obtain a model that satisfy the desired residual behaviours, where the issue we face (autocorrelated residuals) can be critical to our forecast. The main reason behind this could be the lack of data points or the oversimplicity of ETS models.

In terms of out-of-the-sample forecasting, we finalise ETS(M,Ad,A) as our best out-of-sample forecasting method for the UK Electricity Consumption series. Therefore, the ETS(M,Ad,A) model seems to be the best out of all.

***

## 9. Appendix
## 9.1 Why not to proceed with daily electricity demand forecasts
```{r daily_time_plot, fig.width=5, fig.height=4}
# Generating time plot using autoplot()
elec_ts_daily %>% 
  autoplot(demand) + 
  labs(title = "UK Electricity Consumption Daily Time Plot", 
       subtitle = "From Jan 2013 to Dec 2022", 
       y = "Averaged Electricity Demand (GW)", 
       x = "Date") + 
  theme_minimal()
```

From above daily time plot, we have observed a similar trending and seasonal behaviour from that Section 1 suggested. Additionally, we have also observed a large variation in the series itself, which represented the noises in daily series of electricity consumption.

```{r seasonal_plot_weekly}
# Generating weekly seasonal plot using gg_season
elec_ts_daily %>% 
  gg_season(demand, period = "week") + 
  labs(title = "UK Electricity Demand Weekly Seasonal Plot", 
       subtitle = "From Jan 2013 to Dec 2022", 
       y = "Averaged Electricity Demand (GW)", 
       x = "Day of Week") + 
  theme_minimal()
```

Moreover, above seasonal graph demonstrated a discernible dip of electricity consumption during weekends. This shows that in addition to the yearly seasonality that we observed in Section 1, there seems to be a weekly seasonality. The reason behind this could be closure of businesses during weekends.

As a result of the dual seasonality and noises consisted in our daily series, we have decided not to proceed with daily forecasting, due to to inability of basic ETS models on handling such complications. The daily series should be instead modeled with more advanced models (such as the Dual Seasonality Holt-Winters' or ARIMA method), which falls out of the scope of this assignment, therefore, we simply do not consider it.

## 9.2 Seasonal range for each year
```{r seasonality_analysis, fig.width=5, fig.height=4}
# Calculate the differences of seasonal variation for each year
elec_ts_monthly %>% 
  as_tibble() %>% 
  group_by(year = year(month)) %>% 
  summarise(max = max(demand), min = min(demand), 
            diff = round((max - min) * 100 / min, 2)) %>% 
  select(year, diff)
```

## Session Info
```{r}
sessionInfo()
```